\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-09 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
changement .tex sur le modele

\textbf{LIse, 6-09-2021: Je reprends ici}

In this section, we explore the implications of our empirical results on theoretical grounds. While the whole bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation. Specifically, we make use of our empirical results to investigate the welfare consequences of a reduction in international transport costs, when such a reduction also occurs through a reduction in the additive component. \cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020} have preceded us on this issue. We differentiate from them in the following way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive. In contrast, we provide a quantification of such welfare gains, as in \cite{Irrazabal_2015} or \cite{Lashkaripour_JIE2020}. To do so, we rely on our empirical estimates of the transport costs values, that induce a combined decrease in both the ad-valorem and the additive components over the last decades. In a partial-equilibrium model with perfect competition, \cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz' type models. Anticipating on our results, we also share the result, that the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component. As underlined by \cite{Lashkaripour_JIE2020}, one potential explanation relies on the modeling framework. While \cite{Lashkaripour_JIE2020} models a perfectly competitive multi-sector model, we as in \cite{sorensen2014} and \cite{Irrazabal_2015} adopt a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}. In this setting, we indeed show that additive costs do modify the selection of firm on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (4\%, based on early 1980s' value) and the final steady state (6\%, based on 2000's value.)}}}
\end{table}

Following \cite{ghironi}, $f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. The calibration of the fixed export cost obeys the following logic. As in \cite{ghironi}, $f_x$ is endogenously revealed to match a given share of exporting firms at the steady state. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$. Specifically, we endogenously determine the initial value of $f_x$ such that the initial steady state, with 1974 values of transport costs implies a share of exporting firms equal to 4\%, as documented by \cite{BEJK-AER-03}. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 52\% (i.e., from 4\% to 6\%), based on \cite{Lincoln_McCallum2018}.\smallskip

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (2)}\label{tab:calib_TC}
\begin{center}
	\input{table_calibTC_combined.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: In Columns (1), (3), (5) and (7), we model oad-valorem costs only. In Columns (2), (4), (6) and (8), we model both ad-valorem and additive costs. $t$ is calibrated so that the ratio $t/\widetilde{p}_x$ from the model matches its empirical target, with $widetilde{p}^{\text{fas}}_x$ the average fas price set in place by those domestic firms that export. We theoretically define the export fas price through: $p_x = \tau p^{\text{fas}} +t$. TC = Transport Costs, expressed in percentage of the average fas export price.}}}
\end{table}

\textbf{Lise, 06-09-2021: Stop here, changer la calibration}

@@

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs have strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings in two different ways.

First, we run a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario \textit{à la Mélitz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario \textit{à la Hummels}, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components. Importantly, we run this comparative statics analysis \textit{ceteris paribus}, notably with the same value of the export fixed cost $f_x$ as in the initial equilibrium (see Table \ref{tab:calib_horsTC}.

Second, we take into account the fact that the share of exporting firms has substantially increased since the 21\% value reported by \citet{Lincoln_McCallum2018} for 1987. According to \textbf{???}, this share roughly amounts to 35\% in \textbf{???}. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. In the second exercise, we thus run a comparative statics analysis where we contrast the 2014 steady states (e.g., with the 2019 transport costs values) with the two dimensions of trade liberalization: the reduction of transport costs (as in the first exercise) and the reduction of the export fixed cost, consistent with the increase in the share of exporters from 21\% to 35\%.

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (A)-(D)) and Vessel (Columns (E)-(H)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (A)-(B) for Air, (E)-(F) for Vessel), contrasting the case of only ad-valorem costs (Columns (A), (D)) and in presence of additive costs (Columns (B), (F)). Columns (C)-(D) for Air and (G)-(H) for Vessel report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3& 0&	-3.3 \\ \hline
$\Delta \mathcal{W}$ & 0.0202 &  0.0386 & 0.0362 & 0.0540 & 0.0354 & 0.0535 & 0.0467 & 	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	2.393 &	2.207	&3.348	&2.179	&3.382 &	2.872&	4.00   \\\hline
Variety effect (\%)&	-0.827 	&-2.599	&0.747
&-1.038	&-1.323	& -3.123&	-0.126	&-1.902 \\
Price effect (\%)&	2.084 &5.201	& 1.455 &	4.444&	3.568	& 6.829&	 3.001&	6.059 \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In the world including additive costs, we simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

\paragraph{Reduction in international variable transport costs} Based on our empirical estimates, we simulate a reduction in total variable transport costs by 3.4\% in Air transport and 6.4\% in maritime transport, in two different worlds: In a world with only ad-valorem costs (Columns (A) for Air and (D) for Vessel), versus a world with both iceberg and additive transport costs, and where the overall reduction costs comes from both components (Columns (B) for Air and (E) for Vessel).

A first conclusion emerges. Whatever the transport mode (and the associated magnitude of the transport costs decrease), trade liberalization induces welfare gains. Second, the welfare gains are higher when this reduction is partly achieved through a reduction of additive costs. The effect is substantial: The reduction variable transport costs generates a relative welfare gain higher by 1.1 percentage point in Air, 1.2 percentage point in Vessel, when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in iceberg costs only.\smallskip

Recalling that welfare is the inverse of the price index, the explanation can be understood decomposing the welfare change in its two components, the variety effect and the price competitiveness effect. Considering the inverse of Equation (\ref{eq:CPI_vf}), it is straightforward to get the welfare change as:
\begin{equation}
\frac{d\mathcal{W}}{\mathcal{W}_0} = \underbrace{\frac{1}{\sigma-1} \frac{d M_T}{M_{T0}}}_{\text{Variety effect}} +  \underbrace{\frac{d\widetilde{\varphi}_T}{\widetilde{\varphi}_{T0}}}_{\text{Price effect}} \label{eq:decompWelfare}
\end{equation}

We report the decomposition of the welfare gains in their two components (under the various scenarii) in the last two lines of Table \ref{tab:resultats_modele}, as well as visually through Figure \ref{fig:welfare_decomp}. It displays the welfare change and its decomposition between its two components following the reduction in international transport costs, for the decrease estimated in air transport (left column, Panels (1), (1-a) and (1-b)) and in maritime transport (right column, Panels (2), (2-a) and (2-b)). All are expressed in percentage change from the initial steady-state value. In each panel, the blue left bar displays the case where the trade liberalization occurs through a reduction in ad-valorem costs; the grey right bar reporting the case where the (same) reduction in international transport costs occurs through a combined reduction in both the ad-valorem and the additive components, based on our estimated results in 1974 and 2019 (for each transport mode), as in Table \ref{tab:calib_TC}).

\begin{figure}[htbp]
\caption{Welfare decomposition}
\label{fig:welfare_decomp}
\includegraphics[width=15cm, height=12cm]{Welfare_change_bothmodes.pdf}
\begin{minipage} [t]  {7in} \footnotesize%
Notes: All bars are expressed in percentage change from the initial steady-state value.
\end{minipage}
\end{figure}

To go deeper into the analysis, we further decompose each variety and competitiveness effects in its various dimensions, as reported in Figures \ref{fig:variety_air_decomp} (Variety effect) and \ref{fig:competitivity_air_decomp} (Competitiveness effect) for air transport. Figures \textbf{XXX} in \textbf{Appendix} report similar results for maritime transport.

\begin{figure}[htbp]
\caption{Variety effect (Air transport)}
\label{fig:variety_air_decomp}
\includegraphics[width=12cm, height=10cm]{VarietyEffect_air.pdf}
%\begin{minipage} [t]  {7in} \footnotesize%
%Notes: All bars are expressed in percentage change from the initial steady-state value.
%\end{minipage}
\end{figure}

\begin{figure}[htbp]
\caption{Competitiveness effect (Air transport)}
\label{fig:competitivity_air_decomp}
\includegraphics[width=12cm, height=10cm]{CompetEffect_air.pdf}
%\begin{minipage} [t]  {7in} \footnotesize%
%Notes: All bars are expressed in percentage change from the initial steady-state value.
%\end{minipage}
\end{figure}

To understand the changes induced by the additive costs, consider first the benchmark model with only ad-valorem costs, as in \cite{melitz}. In this case, the reduction in transport costs induces an increase in selection on the domestic market, but more domestic firms can now export (Figure \ref{fig:competitivity_air_decomp} for Air transport). Accordingly, the number of domestic active firms reduces, even if a larger number of them is able to export ($M$ decreases but $M_x$ increases, see Figure \ref{fig:variety_air_decomp}). As a whole, the total number of varieties accessible to the consumer reduces (Figure \ref{fig:variety_air_decomp}, $M_T$ decreases slightly). Everything else equal, this reduces welfare (Figure \ref{fig:welfare_decomp}). Yet, this detrimental effect is counteracted by a price competitiveness effect. Due to the tougher selection on the domestic market, the less productive firms no longer enter. As a result, the average productivity on the domestic market increases (Figure \ref{fig:competitivity_air_decomp}, $\widetilde{\varphi}^\ast$ increases), which pushes the average productivity upwards ($\widetilde{\varphi}^\ast$ and $\widetilde{\varphi}_T$ increase). As reported in Figure \ref{fig:welfare_decomp}, the strength of the price competitiveness effect dominates, inducing a increase in welfare following the reduction in iceberg costs, consistently with the analytical results of \cite{melitz}.

What does it change when the reduction in international transport costs also occurs through a reduction in its additive component? As reported in Figure \ref{fig:welfare_decomp} (right grey bars), trade liberalisation still induces welfare gains, and even larger than in the pure ad-valorem case. This is consistent with the analytical results of \cite{sorensen2014}, in a different exercise of trade liberalization though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade liberalization. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.} Quantitatively, the effects are sizeable.

Through which mechanism does it occur? As underlined by \cite{sorensen2014}, a reduction in the additive cost reduces the export-market price of the high-productivity exporters relative to the low-productive ones (this can be shown from Equation (\ref{eq:px})). Within the exporters category, this favors the more productive firms, whose market share, e.g. revenues increases relatively more, as can be shown from Equation (\ref{eq:rx}). Everything else equal, this pushes the average productivity on the export market upwards.\footnote{This mechanism indirectly appears Figure \ref{fig:competitivity_air_decomp}, panel. Given our exercise that assumes a combined decrease in both the additive and the ad-valorem costs, at the general equilibrium, the threshold productivity on the export market $\widetilde{\varphi}^\ast_x$ still decreases, but to a lesser extent when the trade liberalization partly occurs through a reduction in additive costs. } In contrast to ad-valorem costs, the reduction in additive costs induces a \textit{within-exporters selection effect}, in favor of the more productive firms. At the general equilibrium, this within-exporters selection effect also affects the \textit{classic} selection effect at the extensive margin at the heart of the \cite{melitz} model: As the expected export profit increases, it is necessary to be more productive to satisfy the free-entry condition. Everything else equal, the threshold productivity on the domestic market increases, as well as the average productivity. Accordingly, the competitiveness effect increases by more when the trade liberalization involves a reduction in the additive component.

The more negative variety effect (Figure \ref{fig:welfare_decomp}) can be understood as a consequence of the above mechanism. Since the reduction in additive costs favors the more productive firms in terms of market share, entry on the export market is tougher leading to a lower mass of exporters (Figure \ref{fig:variety_air_decomp}). As the selection on the domestic market is also strengthened when trade liberalization involves a reduction in additive costs, the mass of active domestic firms reduces by a larger amount. From the consumer side, this induces a more negative variety effect that is welfare-detrimental everything else equal. As for the pure-iceberg case though, the strength of the competitiveness effect still dominates, inducing positive welfare gains, and even larger when the trade liberalization involves a reduction in additive costs.

\textbf{Faire l'exercice partant d'un monde avec les deux ad-valorem + iceberg, regarder ce qui se passe quand la baisse des coouts totaux est soit soit uniquement iceberg, soit uniquement ad-valorem? Plus proche de l'exercice de Sorensen. Plus clair sur les effets? }

\paragraph{Reduction of the fixed export cost} The above results underline the importance of the additive component of international trade costs. When trade liberalization occurs through a reduction in variable costs, not only the welfare-enhancing effects still apply, but they are even larger. As mentioned by Mélitz final proofs, the reduction in variable costs is not the only form of trade liberalization, which can typically manifest through a reduction in export fixed costs. One might then wonder how additive costs do affect the welfare gains of trade liberalization of this form. Indeed, the reduction in the fixed export costs seems empirically relevant to account for the larger share of exporting firms nowadays relative to the 1970s (Based on XXX, from 19\% in XXX to around 35\% in XXX). As underlined by \cite{melitz} \textbf{JE CROIS QUE C'est DIT DANS FINAL PROOFS, PAS ECTRA. l'a-t-il MONTRE VRAIMENT ANALYTIQUEMENT? A VERIFIER}, the reduction of the fixed export cost is also welfare-enhancing, in presence of yet only ad-valorem variable trade costs. A natural question then emerges: To what extent is this result modified in presence of additive costs? Specifically, are the welfare gains of a fixed export costs decrease larger in presence of additive costs?

>>>>

In this section, we explore the implications of our empirical results on theoretical grounds. While the whole bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation. Specifically, we make use of our empirical results to investigate the welfare consequences of a reduction in international transport costs, when such a reduction also occurs through a reduction in the additive component. \cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020} have preceded us on this issue. We differentiate from them in the following way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive. In contrast, we provide a quantification of such welfare gains, as in \cite{Irrazabal_2015} or \cite{Lashkaripour_JIE2020}. To do so, we rely on our empirical estimates of the transport costs values, that induce a combined decrease in both the ad-valorem and the additive components over the last decades. In a partial-equilibrium model with perfect competition, \cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz' type models. Anticipating on our results, we also share the result, that the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component. As first explanation, it should be noted that, in \cite{Lashkaripour_JIE2020}'s paper, the case with additive costs relies on a share of additive costs that remains negligible. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} models a perfectly competitive multi-sector model, we as in \cite{sorensen2014} and \cite{Irrazabal_2015} adopt a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}. In this setting, we indeed show that additive costs do modify the selection of firm on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (21\%, based on early 1980s' value) and the final steady state (39\%, based on 2000's value.), according to the references provided above. BEJK (2003) refers to \cite{BEJK-AER-03}.}}}
\end{table}

Following \cite{ghironi}, $f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. The calibration of the fixed export cost obeys the following logic. As in \cite{ghironi}, $f_x$ is endogenously revealed to match a given share of exporting firms at the steady state. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$. Specifically, we endogenously determine the initial value of $f_x$ such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, as in  \cite{ghironi} based on the value estimated by \cite{BEJK-AER-03} in the early 1990s. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 85\% (i.e., from 21\% to 39\%), based on the evidence reported in \cite{Lincoln_McCallum2018}.\smallskip

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (2)}\label{tab:calib_TC}
\begin{center}
	\input{table_calibTC_combined.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: In Columns (1), (3), (5) and (7), we model ad-valorem costs only. In Columns (2), (4), (6) and (8), we model both ad-valorem and additive costs. $t$ is calibrated so that the ratio $t/\widetilde{p}^{\text{fas}}_x$ from the model matches its empirical target, with $\widetilde{p}^{\text{fas}}_x$ the average fas price set in place by those domestic firms that export. We theoretically define the export fas price through: $p_x = \tau \widetilde{p}^{\text{fas}} +t$. TC = Transport Costs, expressed in percentage of the average fas export price.}}}
\end{table}

@@

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs have strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings by running a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario so-called \textit{à la Mélitz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario so-called \textit{à la Hummels}, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components. In running this exercise, we also take into account the fact that the share of exporting firms has substantially increased since the 21\% value reported in \cite{BEJK-AER-03} (and consistent with the value estimated by \citet{Lincoln_McCallum2018} for 1987 on US data). According to \cite{Lincoln_McCallum2018}, this share roughly amounts to 39\% in the mid 2000's. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. In our benchmark scenario, we thus run a comparative statics analysis under these two dimensions of trade liberalization: the reduction of transport costs along with the reduction of the export fixed cost.

The results are reported in Table \ref{tab:resultats_modele}, panel (1), by transport mode (for Air (Columns (A)-(B)) and Vessel (Columns (C)-(D) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms. We also run a robustness check of our results by maintaining a fixed export cost value. In this case, the welfare changes are solely attributable to the reduction in the variable transport costs. These results are reported in Table \ref{tab:resultats_modele}, panel (2).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c||c|c}
\hline
Mode & \multicolumn{2}{|c||}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
& (A) & (B) & (C) & (D)  \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-6.4 &-6.4   \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&-6.4&	-3.1	 \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-3.3 \\ \hline \hline
\multicolumn{4}{l}{(1) Lower fixed export cost} \\ \hline
%$\Delta \mathcal{W}$ & 0.0202 &  0.0386 & 0.0362 & 0.0540 & 0.0354 & 0.0535 & 0.0467 & 	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 	\textbf{2.21}	&\textbf{3.35}	&	\textbf{2.87}&	\textbf{4.00 }  \\\hline
Variety effect (\%)&0.75 &-1.04	&-0.13	&-1.90 \\
Price effect (\%)&	1.46 &	4.44&		 3.00&	6.06 \\ \hline \hline
\multicolumn{4}{l}{(2) Constant fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.23&	2.39 & 2.18	&3.38 	 \\ \hline
Variety effect (\%)& -0.83 	&-2.60	&-1.32	& -3.12 \\
Price effect (\%)&2.08 &5.20	&3.57	& 6.83  \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In the world including additive costs, we simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

In line with the literature, we find that trade liberalization induces welfare gains whatever the transport mode (and the associated magnitude of the transport costs decrease). The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction. On that side, the welfare gains are higher when the trade cost reduction occurs through a decrease in the additive component. This conclusion stands in accordance with the analytical results of \cite{sorensen2014}. This is consistent with the analytical results of \cite{sorensen2014}, in a different exercise of trade liberalization though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade liberalization. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.} Quantitatively, the welfare gains are sizeable. The reduction variable transport costs generates a relative welfare gain higher by around 1.25 percentage point when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in iceberg costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). \cite{Irrazabal_2015} also quantify the welfare gains of a trade cost decrease in presence of additive costs. In contrast to \cite{Irrazabal_2015} though, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem). \smallskip

Through which mechanism does it occur? Recalling that welfare is the inverse of the price index, the explanation can be understood decomposing the welfare change in its two components, the variety effect and the price competitiveness effect. Considering the inverse of Equation (\ref{eq:CPI_vf}), it is straightforward to get the welfare change as:
\begin{equation}
\frac{d\mathcal{W}}{\mathcal{W}_0} = \underbrace{\frac{1}{\sigma-1} \frac{d M_T}{M_{T0}}}_{\text{Variety effect}} +  \underbrace{\frac{d\widetilde{\varphi}_T}{\widetilde{\varphi}_{T0}}}_{\text{Price effect}} \label{eq:decompWelfare}
\end{equation}

We report the decomposition of the welfare gains in their two components in Table \ref{tab:resultats_modele}, under our benchmark scenario (Panel (1)) and under constant fixed export costs (Panel (2)).

To understand the changes induced by the additive costs, we start considering the benchmark model with only ad-valorem costs (Table \ref{tab:resultats_modele}, Columns (A) and (C)). As reported in Table \ref{tab:resultats_modele}, the reduction in the iceberg cost induces a negative variety effect, which is yet more than counteracted by a positive competitive effect. The reduction in the number of available varieties for the household stands in line with the insights of the canonical \cite{melitz} model. With the reduction in $\tau$, more firms can now export, but this also increases the expected average profit. This raises the productivity threshold to enter the domestic market. Accordingly, the number of domestic active firms reduces, even if a larger number of them is able to export. As a whole, the total number of varieties accessible to the consumer reduces, which reduces welfare everything else equal.

This detrimental effect is counteracted by a positive price competitiveness effect. Due to the tougher selection on the domestic market, the less productive firms no longer enter. As a result, the average productivity on the domestic market increases, which pushes the average productivity upwards. As reported in Table \ref{tab:resultats_modele}, the strength of the price competitiveness effect dominates, inducing positive welfare gains with the reduction in iceberg costs, consistently with the analytical results of \cite{melitz}.

What does it change when the reduction in international transport costs also occurs through a reduction in its additive component? As underlined by \cite{sorensen2014}, a reduction in the additive cost reduces the export-market price of the high-productivity exporters relative to the low-productive ones (as can be inferred from Equation (\ref{eq:px})). Within the exporters category, this favors the more productive firms, whose market share, e.g. revenues, increases relatively more (see Equation (\ref{eq:rx})). Everything else equal, this pushes the average productivity on the export market upwards. Unlike the ad-valorem costs, the reduction in additive costs induces a \textit{within-exporters selection effect}, in favor of the more productive firms. At the general equilibrium, this within-exporters selection effect also affects the \textit{classic} selection effect at the extensive margin at the heart of the \cite{melitz} model. As the expected export profit increases, it is necessary to be more productive to satisfy the free-entry condition. Everything else equal, the threshold productivity on the domestic market rises, as well as the average productivity. Accordingly, the competitiveness effect increases by more when the trade liberalization involves a reduction in the additive component.

The more negative variety effect also results from the above mechanism. Since the reduction in additive costs favors the more productive firms in terms of market share, entry on the export market is tougher leading to a much more modest increase in the share of exporters. As the selection on the domestic market is also more stringent, the mass of total active firms reduces by a larger amount. From the consumer side, this induces a more negative variety effect that is welfare-detrimental everything else equal. As for the pure-iceberg case though, the strength of the (larger) competitiveness effect still dominates, inducing positive welfare gains, and even larger when the trade liberalization involves a reduction in additive costs.

As mentioned above, our results dwell on the joined reduction in both the variable and the fixed export costs, based on the empirical evidence provided in Section  \ref{sec:basic_results} and in \cite{Lincoln_McCallum2018}. One might yet wonder about the welfare gains induced by the reduction in variable costs only, i.e. \textit{ceteris paribus} for a given value of the fixed export cost. The answer can be found in Table \ref{tab:resultats_modele}, Panel (2). In this case, the fixed export cost is kept constant at its initial value, the only structural change being the decrease in variable transport costs (either ad-valorem only or both additive and ad-valorem). Two results emerge. First, the welfare gains induced by the trade liberalization are lower in magnitude. While this is not a surprising result \textit{per se} (since we only consider the reduction in one source of international frictions, rather than two), this exercise yet delivers a quantification of the welfare gains associated with a reduction in the fixed export cost: They are substantial, by an amount between 0.6 to 1 percentage point depending on the transport mode. Second, the main message of the paper remains valid. The welfare gains of the trade liberalization are still higher when part of this structural change is achieved through a reduction in additive transport costs, by the same order of magnitude (+ 1.25 percentage point). Put it differently, the reduction in the fixed export cost does not seem to depend on the composition of the variable costs. In the end, the welfare gains are the highest when trade liberalization induces a combined reduction in both variable and fixed export costs, and when the reduction in the variable part implies a reduction in the additive component, as observed empirically.\smallskip

In line with \cite{sorensen2014} and \cite{Irrazabal_2015}, our overall theoretical results point out the importance of taking into the additive components of international trade costs. Additive costs have a substantial impact on the extensive margin of trade, by affecting the composition of the basket of exported goods. This, in turn, has important consequences in normative terms. Relying on our empirical estimates of transport costs over 1974-2019, we obtain that the 3.4\% reduction of variable costs in Air transport, combined to the reduction in the fixed export costs, has induced an 3.5\% increase in welfare, much higher than if only iceberg costs were modeled (2.4\%). A similar result applies with the observed 6.4\% in total variable costs in maritime transport along with the reduction in the fixed export costs, with a relative increase in welfare by 4\% (as compared to 3.38\% in a pure ad-valorem world). In a nutshell, we show that neglecting additive costs leads to a substantial underestimation of the welfare gains of trade liberalisation. While this result has been obtained in the canonical \cite{melitz} model, they call for integrating additive costs in New Trade models in view of better assessing the (disputed) question of the welfare gains of trade liberalization.
